The Impact of Critical Slicing in SFL\Comment{tatistical Fault Localization}

### 2018-11-10 paper/main.tex
pass on section 3

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in fault~\cite{FLSurvey2016,
  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{r}{0.29\textwidth}
  \vspace{-2ex}
  \hspace{-3ex}
  \centering
  \small
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}
Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed:
%
\begin{equation}\label{eq:occurrence}
 n_{pq}(j) = |\{i\mid \A{ij}=p \wedge e_i=q\}|
\end{equation}
%
%\noindent
$n_{pq}(j)$ denotes the number of runs in which the
component $j$ has been active during execution ($p = 1$) or not
($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
For instance, $n_{11}(j)$ counts the number of times component $j$ has
been involved ($p = 1$) in failing executions ($q = 1$), whereas
$n_{10}(j)$ counts the number of times component $j$ has been involved
in passing executions. We then calculate similarity to the error
vector by means of applying \emph{fault predictors} to each component
to produce a score quantifying how likely it is to be faulty.
Components are then ranked according to such likelihood scores and
reported to the user. \Fix{show ochiai here...}

\Mar{----------------------- estou aqui}

\section{Dynamic Slicing + \sfl{}}
\label{sec:combination}

The methodology we used to combine dynamic slicing with \sfl{}
consists of the following steps: (1) Compute the execution spectra as
discussed in Section~\ref{sec:sfl}, (2) Compute slices associated with
tests, (3) Adjust the spectra computed in Step 1 with results obtained
in Step 2, and (4) Compute suspiciousness
scores. Figure~\ref{fig:illustration} illustrates the process of
updating the spectra and suspiciousness ranking as result of slicing
the program against the failing test $t_2$.  The faulty statement in
this example is the component $c_2$.

@@

\begin{figure}[h!]
  \centering
{\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
   \begin{tabular}{c|ccccc|c}
     $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
     $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
     $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
     $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
     $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
     $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
     \hline
   \end{tabular}
   \quad
   $\Rightarrow$
   \quad
   \begin{tabular}{c|ccccc|c}
     $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
     $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
     $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
     $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
     $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
     $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
     \hline
   \end{tabular}

   \vspace{3ex}

   \begin{tabular}{cccccc}
     & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$  \\
     & 0.32 & 0.35 & 0.55 & 0.59 & 0.32 \\
   \end{tabular}
   \quad
   $\Rightarrow$
   \quad
   \begin{tabular}{cccccc}
     & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$  \\
     & 0.32 & 0.35 & {\cellcolor{Gray}0.29} & {\cellcolor{Gray}0.32} & 0.32 \\
   \end{tabular}

 }
\caption{Illustration of spectra and ranking update.}
\label{fig:illustration}
\end{figure}

The slice obtained from $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
enables identification of cells in the matrix (/spectra) whose values
can be set to zero. In general, updates in the matrix results in an
increase of suspiciousness for a given component when the target test
is passing or a reduction of suspiciousness when the target test is
failing. Consider the Ochiai formula~\cite{DBLP:conf/prdc/AbreuZG06}

\[
\frac{\N{11}}{\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}}}
\vspace{1ex}\], where $n_{pq}(j)$ is the number of runs in which the
component $j$ has been active during execution ($p = 1$) or not
($p=0$), and in which the runs failed ($q = 1$) or passed ($q = 0$).
Slicing of a failing test reduces the value of $\N{11}$ and increases
the value of $\N{01}$ for those statements $j$ which are not part of
the slice. Therefore, suspiciosness of those statements decrease. In
this example, components $c_3$ and $c_4$, which are not in the slice
of $t_2$, have their suspiciousness reduced, enabling the faulty
component $c_2$ to rise from the third to the first position in the
ranking.

\Fix{I suggest to add an algorithm section and perhaps a discussion on
time/space complexity.}

@@

>>>>

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in fault~\cite{FLSurvey2016,
  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{r}{0.29\textwidth}
  \vspace{-2ex}
  \hspace{-3ex}
  \centering
  \small
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}
Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well~\Fix{cite}. The Ochiai
formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
$\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10})}$.

\section{Critical Slicing + \sfl{}}
\label{sec:combination}

The combinination of critical slicing and \sfl{} consists of the
following steps: (1) Compute the execution spectra as discussed in
Section~\ref{sec:sfl}, (2) Compute slices associated with failing
tests, (3) Adjust the spectra computed in Step 1 with results obtained
in Step 2, and (4) Compute suspiciousness
scores. Figure~\ref{fig:illustration} illustrates the update of the
spectra and suspiciousness rankings as result of slicing the program
against the failing test $t_2$. The faulty statement in this example
is the component $c_2$.  The slice obtained from $t_2$ is $\{c_2,
c_5\}$.  Intuitively, slicing enables identification of cells in the
matrix (/spectra) whose values can be set to zero.

@@

\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.5\textwidth}  
    {\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
      \begin{tabular}{c|ccccc|c}
        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
        $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
        \hline
      \end{tabular}
      \quad
      $\Rightarrow$
      \quad
      \begin{tabular}{c|ccccc|c}
        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
        $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
        \hline
      \end{tabular}
    }
    \caption{Spectra update.}
  \end{subfigure}

  \vspace{2ex}

  \begin{subfigure}{0.5\textwidth}
    \centering
    \begin{tabular}{cccccc}
      1 & $c_4$ (0.59) & & 1 & $c_2$ (0.35) \\
      2 & $c_3$ (0.55) & & 2.5 & $c_1$ (0.32)\\
      3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
      4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
      4.5 & $c_5$ (0.32) & & 5 & $c_3$ (0.24)\\
    \end{tabular}
    \caption{Ranking update.}
  \end{subfigure}

  \caption{Modifications on spectra and ranking as result of slicing code against test $t_2$.}
  \label{fig:illustration}
\end{figure}

%% In general, updates in the matrix results in an increase of
%% suspiciousness for a given component when the target test is passing
%% or a reduction of suspiciousness when the target test is failing.

\begin{theorem}
  The rank of faulty statements cannot decrease if the slice includes
  the faulty statements.
\end{theorem}

For those statements $j$ which are not part of the slice of a failing
test, the combination reduces the value of $\N{11}$ and increases the
value of $\N{01}$. Therefore, suspiciosness of those statements
decrease. In this example, components $c_3$ and $c_4$, which are not
in the slice of $t_2$, have their suspiciousness reduced, enabling the
faulty component $c_2$ to rise from the third to the first position in
the ranking. \Mar{what about other formula?}

\Mar{think of another theorem...}

@@

\Mar{-------------------- estou aqui}
